Understanding GDP relations to Crime in US Cities

### 2017-03-08 resource/index.Rmd
worked on RMD

```{r, echo=FALSE}
  colnames(cities.all)
```

@@

```{r, echo=FALSE}
  gdp[1:5,] %>% 
  select_("gdp_2010", "gdp_2011", "gdp_2012", "gdp_2013", "gdp_2014", "gdp_2015", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015") %>% 
  kable()
```

@@

```{r, echo=FALSE}
  dim(gdp %>% 
  select_("gdp_2010", "gdp_2011", "gdp_2012", "gdp_2013", "gdp_2014", "gdp_2015", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"))
```

@@

```{r, echo=FALSE}
  colnames(gdp %>% 
  select_("gdp_2010", "gdp_2011", "gdp_2012", "gdp_2013", "gdp_2014", "gdp_2015", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"))
```

```{r, echo=FALSE}
  sapply(gdp %>% 
  select_("gdp_2010", "gdp_2011", "gdp_2012", "gdp_2013", "gdp_2014", "gdp_2015", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"), typeof)
```

@@

>>>>

@@

```{r, echo=FALSE}
  gdp[1:5,] %>% 
  select_("X2010_gdp", "X2011_gdp", "X2012_gdp", "X2013_gdp", "X2014_gdp", "X2015_gdp", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015") %>% 
  kable()
```

@@

```{r, echo=FALSE}
  dim(gdp %>% 
  select_("X2010_gdp", "X2011_gdp", "X2012_gdp", "X2013_gdp", "X2014_gdp", "X2015_gdp", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"))
```

@@

```{r, echo=FALSE}
  colnames(gdp %>% 
  select_("X2010_gdp", "X2011_gdp", "X2012_gdp", "X2013_gdp", "X2014_gdp", "X2015_gdp", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"))
```

```{r, echo=FALSE}
  sapply(gdp %>% 
  select_("X2010_gdp", "X2011_gdp", "X2012_gdp", "X2013_gdp", "X2014_gdp", "X2015_gdp", "gdp_per_person_2010", "gdp_per_person_2011",	"gdp_per_person_2012",	"gdp_per_person_2013", "gdp_per_person_2014",	"gdp_per_person_2015"), typeof)
```

@@

##### What all this means? 
The main purpose of combining these two data sets was to determine if there was some sort of correlation between a cities Gross Domestic Product and the amount of crime that happens within it.

``` {r echo=FALSE}

```
